%-------------------------------------------------------------------------------
% 
\chapter*{Abstract}
\pdfbookmark[0]{Abstract}{Abstract}
%-------------------------------------------------------------------------------
%1. Knowledge acquisition is an important part of Artificial Intelligence. It is a difficult task that has been attempted for several decades through hand-annotation and structuring by human experts. In recent years, there have been attempts to scale this type of approach through crowdsourcing.

%2. Crowdsourcing high quality knowledge is expensive and noisy (despite recent advances in technology, and a broad availability of manpower).

%3. Through a novel set of knowledge acquisition tools, natural language user interaction, and a rich background knowledge base, you propose a system that can significantly reduce the cost of acquiring knowledge, and increase the quality of knowledge--creating a virtuous cycle. STATE HOW MUCH YOU REDUCE THE COST, AND HOW MUCH YOU INCREASE THE QUALITY.

%4. You propose a concrete implementation of the proposed system that has been tested over multiple years with thousands of users, yielding very promising results. STATE HOW WELL THIS SYSTEM WORKS QUANTITATIVELY.

Knowledge Acquisition is an important part of Artificial Intelligence. Having high quality structured knowledge helps to advance other research activities that depend on a rich understanding of the world around us. Due to a lack of reliable automation strategies this problem has been mostly attacked through hand-annotation and structuring by human experts. In recent years, there have been attempts to scale the manual approach through crowd-sourcing.

Although numerous systems and methods for crowd-sourced knowledge acquisition have been developed to solve the problem of manpower, the issues of high cost, task specification, targeting, consistency, and eventual quality of acquired knowledge, seem to persist.

This thesis addresses these issues by formalising and implementing an approach to scalable human-driven knowledge acquisition that significantly reduces the costs involved, and increases the quality of acquired knowledge. Through a novel set of tools, natural language user interaction, and a rich background knowledge base, our approach uses contextual clues to pick the right users at the right time: leveraging existing knowledge to check the consistency of user-provided answers. Newly acquired knowledge is incorporated into the knowledge base, creating a virtuous cycle whereby the knowledge acquisition process and the acquired knowledge are constantly improving through time. The proposed approach can be incorporated into natural language human-computer Interaction (HCI) interfaces to add high quality, cost-effective knowledge acquisition capabilities to almost any system with a distributed user base.

We propose a concrete implementation of the system, which has been tested over multiple years with thousands of users, yielding very promising results. During the test run, we collected over 57,978 answers, resulting in 386,980 new assertions. Evaluation shows the extracted knowledge to be true and useful 95\% of the time. Furthermore, using context to pro-actively drive knowledge acquisition increased engagement and effectiveness (the number of new assertions/day/user) by 175\% over the baseline.