%-------------------------------------------------------------------------------
% 
\chapter*{Acknowledgments}
\pdfbookmark[0]{Acknowledgments}{Acknowledgments}
%-------------------------------------------------------------------------------
I would like to express great appreciation to my PhD supervisor Prof. Dunja 
Mladenić for her support, guidance and advice throughout my studies. 
I would like to thank my coauthors, collaborators and
my colleagues from Jožef Stefan Institute, especially James Hodson, Blaz Fortuna, Jan Rupnik for many valuable discussions, 
insights and suggestions. 
I would also like to thank the members of my doctoral committee, 
Michael Witbrock, Tomaž Erjavec and Iztok Savnik for their valuable comments and
remarks. 
Special thanks go to Michael Witbrock, Janez Starc and Dane Sulič for
multiple years of help with the design and development of Curious Cat 
implementation. I thank to all of our 728 users who contributed 
to the experiment of this KA system, and Dr. Dave Schneider in particular, 
Cycorp management and members of the Cycorp technical staff (including Chris 
Deaton and Dr. David Baxter) more generally for licensing, for their kind 
assistance with APIs, KR advice and other help as we constructed and 
tested Curious Cat.
Additionally I would like to thank Marko Grobelnik and colleagues from
Artificial Intelligence Laboratory (Jožef Stefan Institute) for providing a 
good work and research environment, enabling me to focus on the research and
implementation required to finish this thesis. Similar thanks goes to AI team
at Bloomberg L.P., for encouragement and allowing me to abstain from my work
duties while focusing on the thesis.

Finally I wish to thank Vanessa, my parents Agata and Bernard and my brothers
Marko and Valter for their support and encouragement.

\rule{0.5\textwidth}{.4pt}

This work was supported and partially financed by European Commission under
LARKC (The Large Knowledge Collider: a platform for large scale integrated
reasoning and Web-search, FP7-215535), MOBIS (Personalized Mobility Services 
for energy efficiency and security through advanced Artificial Intelligence 
techniques, FP7-318452), ENVISION (EmpoweriNg European SME business model 
Innovation, ICT-2009-249120), OPTIMUM (Multi-source Big Data Fusion Driven 
Pro-activity for Intelligent Mobility, H2020-MG-636160) and personally by 
Dr. Michael Witbrock.

\rule{0.5\textwidth}{.4pt}

Parts of this thesis were originally published as \emph{Curious Cat-Mobile, 
	Context-Aware Conversational Crowdsourcing Knowledge Acquisition} in 
\emph{ACM Trans. Inf. Syst.}